### 2022-02-14 src/text/1-introduction.tex
added preliminary GADF paragraph in the intro and corresponding references

The Cherenkov Telescope Array will be operated as an open observatory for the
first time. Thus there is a need for open analysis software as well.

Once the primary photons are reconstructed the format of the data of all
Gamma-ray instrumets can be brought into a common format. An effort is the
gamma-astro data formats~\cite{gadf-zenodo}. The data format is based on FITS
\citep{fits}.

>>>>

The Cherenkov Telescope Array (CTA) will be operated as an open observatory for the
first time. Thus there is a need for open analysis software as well.

Moreover, the operation of CTA as an observatory introduces the necessity of sharing
its data publicly. The data-reduction workflow of different IACTs of the current
generation is remarkably similar, resulting in a ``high'' data level that can be
finally used to derive scientific results (e.g. spectra, sky maps, light curves).
The information in this high data level is independent on the data reduction,
and eventually of the detection technique. This implies, for example, that data
from IACT and WCD can be represented within the same model.
The efforts to prototype the future CTA data model and to convert current IACT
data in a format usable with the newly-available science tools converged in the 
so-called ``Data Format for Gamma-ray Astronomy'' initiative
\citep{gadf_proc, gadf_universe}, abbreviated in \texttt{gamma-astro-data-format}
(GADF). The latter proposes prototypical specifications to produce files based
on the flexible image transport system (FITS) format \citep{fits} encapsulating
this high-level information. This is realized by storing a list of gamma-like
events with their measured quantites (energy, direction, arrival time) and a
parametrisation of the response of the system (see Sec.~\ref{ssec:gammapy-data}
and Sec.~\ref{ssec:gammapy-irf} for more information).
